---
title: "Tracking our way out of COVID-19 in Texas"
description: |
  With vaccine rollouts well underway, ending the chaos of coronavirus requires tracking the path charted by officials to the finish line
author:
  - last_name: Worthington
    first_name: Matt
    url: https://github.com/mrworthington
    affiliation: The LBJ School of Public Affairs
    affiliation_url: https://lbj.utexas.edu
date: 1-20-2020
output:
  distill::distill_article:
    css: welcome_header.css
    self_contained: false
preview: erik-mclean-nOQO6Z-Q0Ig-unsplash.jpg
# categories:
#   - public health
#   - dygraphs
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(janitor)
library(highcharter)
library(lbjdata)
# Learn more about creating blogs with Distill at:
# https://rstudio.github.io/distill/blog.html


```

When COVID-19 first began creeping through the United States in late February, search interest for the 2011 box-office thriller ["Contagion"](https://en.wikipedia.org/wiki/Contagion_(2011_film)) began skyrocketing as a search term on Google Trends. With a total run-time of 1 hour and 46 minutes, the film follows the spread of a novel virus that rapidly circulates across the globe, wreaking havoc on the world's public health and its economy. Like our own pandemic, a vaccine is pursued throughout the film and---spoiler-alert---ultimately delivered. Despite its countless similarities, the most notable difference between the world of Contagion and the world of COVID-19 is the vaccine rollout, which only accounts for less than 20% of the movie.


```{r echo=FALSE, layout="l-screen"}

color_theme <- "#005f86" # extracted with chrome extension

read_csv("raw_data/contagion_google_trends.csv", skip=1) %>%
  clean_names() %>% 
  hchart("areaspline", 
         hcaes(x=week, y =contagion_united_states),
         marker = list(enabled=FALSE),
         name = "Interest Score: ") %>% 
  hc_title(text="Searches for 'Contagion' on Google Trends") %>% 
  hc_add_theme(hc_theme_lbj(header_align = "center")) %>% 
  hc_tooltip(
    pointFormat = "<span  style='color: {series.color}'> {series.name} <b>{point.y}</b><br/></span>",
    shadow = FALSE,
    backgroundColor = "transparent",
    style = list(textOutline = "3px #fff"),
    borderColor = "transparent",
    borderWidth = 0
  ) %>% 
  hc_xAxis(
    title = list(text = NULL),
    opposite = TRUE,
    gridLineWidth = 1,
    gridLineOpacity = 0.5,
    gridLineColor = "rgba(0, 95, 134,0.3)", # vertical lines
    tickColor = "rgba(0, 95, 134,0.5)",
    lineColor = "transparent",  # horizontal line,
    labels = list(style = list(color = color_theme, opacity = 0.8, fontSize = "16px"))
    # tickInterval = 8 * 24 * 3600 * 1000 # interval of 1 day (in your case = 60)
    ) %>%
  hc_yAxis(
    title = list(text = ""),
    opposite = TRUE,
    max = 100,
    maxPadding=10,
    gridLineColor = "transparent",
    showFirstLabel = FALSE,
    labels = list(
      style = list(color = color_theme, fontSize = "16px"),
      align = "left",
      x = -100
    )
  ) %>%
  hc_plotOptions(
    series = list(
      color = color_theme,
      fillColor = hex_to_rgba(color_theme, 0.20),
      marker = list(enabled = FALSE)
    )
  ) %>%
  hc_chart(
    spacingBottom =  0,
    spacingLeft =  -6,
    spacingRight =  -55 # just plying to get these numbers
  ) %>% 
  hc_size(height = 300) %>% 
  # hc_title(text = "Diamonds Are Forever") %>%
  hc_subtitle(text = "Source: Diamonds data set") %>%
  hc_credits(enabled = TRUE,
             text = "Source: Google Trends - 'Contagion' Search Term.",
             href = "https://trends.google.com/trends/explore?hl=en-US&tz=360&geo=US&q=contagion&sni=3")
```
