---
title: "Explore Pace"
description: |
  How fast are we distributing COVID-19 Vaccines? <ul class="list-inline title-nav"> 
  <li class="list-inline-item-nav"><div class = "go-to-nav" >Go to: </div></li>
  <li class="list-inline-item-nav">
    <a href="providers.html"> <button type="button" class="btn btn-outline-light mb-2"> Providers </button> 
    </a>
  </li>
  <li class="list-inline-item-nav">
    <a href="equity.html"> <button type="button" class="btn btn-outline-light mb-2"> Equity </button> 
    </a>
  </li>
  </ul>
output: 
  distill::distill_article:
    toc: true
    css: pace_header.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set()
library(gt)
library(tidyverse)
library(ggforce)
library(highcharter)
library(readxl)
library(janitor)
library(reactable)
library(htmltools)
library(tippy)
library(lbjdata)
library(zoo)

today <- Sys.Date()
today_lbl <- format(Sys.Date(), format = "%b %d, %Y")
time_lbl <- format(Sys.time(), format = "%I:%M %p")

src <- "https://dshs.texas.gov/immunize/covid19/COVID-19-Vaccine-Data-by-County.xls" # URL For Daily COVID Data
lcl <- basename(src)
filepath <- paste0("raw_data/", today,"_",lcl,"x")
download.file(url = src, destfile = filepath) # Downloads The Data

src_providers <- "https://genesis.soc.texas.gov/files/accessibility/vaccineprovideraccessibilitydata.csv"
lcl_providers <- basename(src_providers)
filepath_providers <- paste0("raw_data/",today,"_",lcl_providers)
download.file(url = src_providers, destfile = filepath_providers)


with_tooltip <- function(value, tooltip, ...) {
  div(style = "text-decoration: underline; text-decoration-style: dotted; cursor: help",
      tippy(value, tooltip, ...))
}

bar_chart <- function(label, width = "100%", height = "16px", fill = "#005f86", background = NULL) {
  bar <- div(style = list(background = fill, width = width, height = height))
  chart <- div(style = list(flexGrow = 1, marginLeft = "8px", background = background), bar)
  div(style = list(display = "flex", alignItems = "center"), label, chart)
}


vaccine_hc <- hc_theme_merge(
  hc_theme_smpl(),
  hc_theme(chart = list(backgroundColor = "#fff", 
                        style = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif', 
                                     fontSize = "28px",  fontWeight = "bold",
                                     color="#333f48", textTransform="initial")),
           title = list(style = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif', 
                                     fontWeight="bold",
                                     color="#333f48"),
                        align = "left"), 
           subtitle = list(style = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif',
                                        color="#7d7d7d",
                                        textTransform="initial",
                                        fontWeight="400",
                                        fontSize = "14px"),
                           align = "left"), 
           legend = list(align = "right", 
                         style = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif', color="#6d6d6d"),
                         itemStyle = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif', color = '#6d6d6d'),
                         itemHoverStyle = list(color = 'gray'),   
                         verticalAlign = "top"),
           credits = list(style = list(color = "#8d8d8d")),
           xAxis = list(labels =list(style = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif', color="#2d2d2d")), 
                        title = list(style = list(color = "#333f48", fontSize = "12px", 
                                                  color="#333f48",fontWeight="500")),
                        gridLineWidth = 0,
                        gridLineColor = "#9d9d9d", 
                        lineColor = 'rgba(0,0,0,0.7)', 
                        minorGridLineColor = 'rgba(0,0,0,0.7)', 
                        tickColor = "#9d9d9d", 
                        tickWidth = 1), 
           yAxis = list(labels =list(style = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif', color="#2d2d2d")), 
                        title = list(style = list(color = "#333f48", fontSize = "12px", 
                                                  color="#333f48",fontWeight="500")), 
                        gridLineWidth = .5,
                        gridLineColor = 'rgba(0,0,0,0.15)', 
                        lineColor = 'rgba(0,0,0,0.15)', 
                        minorGridLineColor = 'rgba(0,0,0,0.15)', 
                        tickColor = "#9d9d9d", 
                        tickWidth = 2)))

library(gghighlight)

states <- tigris::states(cb=TRUE) %>% 
  as_tibble() %>% 
  clean_names() %>% 
  select(statefp, name) %>% 
  arrange(statefp) %>% 
  slice(1:51) %>% 
  mutate(name = str_replace(name, "New York", "New York State"))
  
```


# Pace Overview

## Texas Summary

The chart attempts to capture a holistic snapshot of multiple data points related to state's current efforts to vaccinate the population. At a high level, this chart is a single box that represents everyone in Texas aged 12 years and older. Within the box, you can see how much of is made up of eligible phases and how much of it is made up of the remaining population aged 12 years and older. And then, two lines mark the following:

* **Doses Shipped:** How many doses have been shipped compared to the entire 12+ population?
* **Persons Fully Vaccinated:** How many people have been fully vaccinated compared to the entire 12+ population?

```{r state summary, echo=FALSE, fig.width=11, layout="l-page"}

vaccine_summ <- read_excel(filepath, sheet = "By County", skip=0) %>% 
  clean_names() %>% 
  filter(county_name=="Texas") %>%
  mutate(across(total_doses_allocated:population_education_and_child_care_personnel, as.numeric)) %>% 
  select(county_name, population_16, people_fully_vaccinated, total_doses_allocated, 
         starts_with("population_phase_"), population_16_64_any_medical_condition, 
         population_education_and_child_care_personnel) %>% 
  mutate(population_phase_remaining = population_16 - (population_phase_1a_healthcare_workers +
                                                       population_phase_1a_long_term_care_residents +
                                                       population_16_64_any_medical_condition +
                                                       population_education_and_child_care_personnel),
         remaining_box_start = population_16 - population_phase_remaining) %>%
  rename(`Phase 1A - Healthcare Workers`=population_phase_1a_healthcare_workers, 
         `Phase 1A - Long Term Care`=population_phase_1a_long_term_care_residents, 
         `Phase 1B - 65+ and High Risk`=population_16_64_any_medical_condition,
         `School & Child Care Personnel`=population_education_and_child_care_personnel,
         `Future Phases`=population_phase_remaining) %>%
  pivot_longer(cols=c(contains("Phase"), "School & Child Care Personnel"), names_to = "phase_pop_est", values_to = "value") %>%
  mutate(order = case_when(
    phase_pop_est == "Phase 1A - Healthcare Workers" ~ 1,
    phase_pop_est == "Phase 1A - Long Term Care" ~ 2,
    phase_pop_est == "Phase 1B - 65+ and High Risk" ~ 3,
    phase_pop_est == "School & Child Care Personnel" ~ 4,
    phase_pop_est == "Future Phases" ~ 5
  )) %>% 
  arrange(order) %>% 
  mutate(
  prev_1 = lag(value, 1),
  prev_2 = lag(value, 2),
  prev_3 = lag(value, 3),
  prev_1 = replace_na(prev_1, 0),
  prev_2 = replace_na(prev_2, 0),
  prev_3 = replace_na(prev_3, 0)) %>% 
  mutate(lab_pos = (value/2) + (prev_1 + prev_2 + prev_3)) 

box_start <- unique(vaccine_summ$remaining_box_start)
box_end <- unique(vaccine_summ$population_16)
fully_vac_lbl <- scales::comma(unique(vaccine_summ$people_fully_vaccinated), scale = .000001, accuracy = 0.01, suffix = "m")
shipped_lbl <- scales::comma(unique(vaccine_summ$total_doses_allocated), scale = .000001, accuracy = 0.01, suffix = "m")
fully_vac_xend <- unique(vaccine_summ$people_fully_vaccinated)
shipped_xend <- unique(vaccine_summ$total_doses_allocated)

vaccine_summ %>%
  ggplot() +
  geom_col(data = . %>%  slice(1), aes(y=county_name, x=population_16), fill = "#333f48", alpha = .05) +
  geom_col(data = vaccine_summ, aes(y=county_name, x=value, fill = reorder(phase_pop_est,desc(order))), alpha=.8) +
  # annotate(geom = "rect", alpha = 0, color = "#333f48", linetype = 2, 
  #          xmin = box_start, xmax = box_end, ymin = .55, ymax = 1.45) +
  geom_text(data = . %>% filter(phase_pop_est != "Future Phases"), angle=90, color="white", size = 3, family = "Graphik-Semibold",
            aes(y=county_name, x=lab_pos, label = reorder(phase_pop_est,desc(order)))) +
  geom_text(data = vaccine_summ %>% filter(phase_pop_est == "Future Phases"), color="#2d2d2d", size = 6,  hjust = 0.35,
            family = "Graphik-Semibold", aes(y=county_name, x=lab_pos), label = "Phase 1C + Pop. (12+)") +
  geom_vline(aes(xintercept=total_doses_allocated), linetype = 2, size = .9, color = "#2d2d2d") +
  geom_vline(aes(xintercept=people_fully_vaccinated), linetype = 2, size = .9, color = "#2d2d2d") +
  scale_x_continuous(labels = scales::unit_format(unit = "M", accuracy = 1, scale = 1e-6)) +
  scale_fill_manual(values = c("#d6d2c4","#333f48","#005f86",  "#9cadb7","#bf5700")) +
  guides(fill=guide_legend(title = "Legend",
                           keyheight = .8)) +
  annotate(
    geom = "curve", color = "#2d2d2d", x = shipped_xend*.85, y = 1.55, xend = shipped_xend*.99, yend = 1.5,
    curvature = -.1, arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(geom = "label", x = shipped_xend*.65, y = 1.53, color = "#2d2d2d", 
           label = glue::glue("Doses Shipped: {shipped_lbl}"), family = "Graphik", hjust = "left") +
  annotate(
    geom = "curve", color = "#2d2d2d", x = fully_vac_xend*1.55, y = .48, xend = fully_vac_xend*1.05, yend = .54 , 
    curvature = -0.1, arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(geom = "label", x = fully_vac_xend*1.54, y = .48, color = "#2d2d2d", 
           label = glue::glue("Persons Fully Vacinated: {fully_vac_lbl}"), family = "Graphik", hjust = "left") +
  theme_minimal(base_family = "Graphik") +
  theme(plot.title = element_text(family = "Graphik-Bold", color = "#333f48", size =20),
        plot.subtitle = element_text(family = "Graphik-Regular", color = "#333f48", margin = margin(b=15)),
        panel.grid.major.y = element_blank(),
        plot.margin = margin(t=15, r=15, b=10, l = 15),
        axis.text.y = element_blank(),
        legend.position = "none") +
  labs(title = "Texas Summary of Vaccination Progress",
       subtitle = paste0("Source: Texas Department of State Health Services. Last pulled on ", today_lbl, " at ", time_lbl),
       x = NULL,
       y = NULL,
       color = NULL,
       caption = "Data File: 'Accessible Vaccine Dashboard Data'\nLink: https://dshs.texas.gov/immunize/covid19/COVID-19-Vaccine-Data-by-County.xls\nChart by: @mrworthington")
  ggsave(paste0("figures/",today,"_","tx_vaccine_summary.png"), dpi = 300, width = 11, height = 4.5)

```

```{r daily-dose-chart-all, echo=FALSE, fig.height=18, layout="l-page"}

library(quantmod)

vaccine_summ_daily_tot <- read_excel(filepath, sheet = 4, skip=0, col_types = c("text", "date", "numeric")) %>% 
  clean_names() %>% 
  filter(age_group!="Grand Total") %>% 
  group_by(date=vaccination_date) %>%
  summarise(daily_doses = sum(doses_administered)) %>% 
  mutate(date=as.Date(date)) %>% 
  mutate(new_doses_7_day_avg= rollmean(daily_doses, 7, fill =0,
                                   align = "right")) %>%
  mutate(date = as.Date(date, format("%b %d %Y"))) %>% 
  ungroup() %>% 
  drop_na()

vaccine_summ_daily <- read_excel(filepath, sheet = 4, skip=0, col_types = c("text", "date", "numeric")) %>% 
  clean_names() %>% 
  filter(age_group!="Grand Total") %>% 
  group_by(age_group,date=vaccination_date) %>%
  arrange(age_group) %>%
  summarise(daily_doses = sum(doses_administered)) %>% 
  mutate(date=as.Date(date)) %>% 
  mutate(new_doses_7_day_avg= rollmean(daily_doses, 7, fill =0,
                                   align = "right")) %>%
  mutate(date = as.Date(date, format("%b %d %Y"))) %>% 
  ungroup() %>% 
  drop_na()

  hcoptslang <- getOption("highcharter.lang")
  hcoptslang$thousandsSep <- ","
  options(highcharter.lang = hcoptslang)
  
myMenuItems <- c("downloadCSV", "downloadXLS","separator", "downloadPNG", "downloadJPEG", "downloadPDF", "downloadSVG")

highchart(type = "stock") %>% 
      hc_add_series(vaccine_summ_daily, type = "column", hcaes(x = date, y = daily_doses, group = age_group),
                    tooltip = list(pointFormat = "{point.age_group}: {point.daily_doses:,.0f}")) %>%
      hc_add_series(vaccine_summ_daily_tot, type = "area", hcaes(x = date, y = new_doses_7_day_avg),
                    tooltip = list(pointFormat = "7-Day Avg.: {point.new_doses_7_day_avg:,.0f}"),
                    color = "#bf5700", name="7-Day Avg.") %>% 
      hc_plotOptions(area = list(fillOpacity=.1),
                     series = list(stacking = "normal")) %>% 
      hc_title(
        text ="Daily Administered Doses - Texas",
        useHTML = TRUE) %>%
hc_subtitle(
        text =paste0("Shown are the number of reported daily administered doses across the state of Texas and the 7-day average of daily adminsitered doses. Data last pulled on ",today_lbl," at ", time_lbl,".<br>LEGEND - <span style='color: #bf5700'>7-DAY ROLLING AVG.</span>"),
        useHTML = TRUE) %>% 
      hc_yAxis(title = list(text ="New Doses Administered Per Day", style = list(color = "#333f48", fontSize = "12px", 
                                                  color="#333f48",fontWeight="500")),
               min = min(vaccine_summ_daily_tot$daily_doses),
               max = max(vaccine_summ_daily_tot$daily_doses),
               labels =list(style = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif', color="#2d2d2d"))) %>% 
      # hc_xAxis(title=NULL,
      #          plotLines=plotLines) %>% 
      hc_tooltip(table = TRUE, sort = TRUE,
                 pointFormat = "<b>{point.name}</b>
                   New Doses: {point.y:,.0f}") %>%
      hc_colors(colors = list('#1170aa', '#c85200','#ffbc79','#57606c','#5fa2ce')) %>% 
      hc_legend(enabled=TRUE) %>% 
      hc_credits(
        enabled = TRUE,
        text = "Source: Texas DSHS - COVID-19 Accessible Vaccine Dashboard Data",
        href = "https://dshs.texas.gov/immunize/covid19/COVID-19-Vaccine-Data-by-County.xls") %>%
      hc_add_theme(lbjdata::hc_theme_lbj()) %>% 
      hc_rangeSelector(allButtonsEnabled= FALSE, enabled = TRUE, 
                       verticalAlign = "top",
                       selected = 3, inputBoxBorderColor= 'white') %>% 
      hc_exporting(enabled=TRUE, scale=2, sourceHeight = 900,allowHTML = TRUE)

```


<!-- ## National Comparison -->

```{r ggplot2 national comparison, eval=FALSE, fig.height=4.5, fig.width=11, message=FALSE, warning=FALSE, include=FALSE, layout="l-page"}

library(RSocrata)

cdc_vaccine_summary <- read.socrata("https://data.cdc.gov/resource/unsk-b7fc.csv") |> 
  filter(date==as.Date(max(date))) |> 
  select(date:location, contains("100k"), contains("pct"))

cdc_last_update <- "May 10, 2021"
cdc_last_time <- "6:00AM"

cdc_vaccine_summary <- read_csv("raw_data/covid19_vaccinations_in_the_united_states-14.csv",
                                skip = 2, na = "N/A") %>% 
  clean_names() %>% 
  select(area=state_territory_federal_entity, contains("_per_100k"), starts_with("percent"), -contains("18")) %>%
  drop_na(doses_delivered_per_100k)

cdc_vaccine_summary_ggplot2 <- cdc_vaccine_summary %>% 
  mutate_at(vars(contains("_per_100k")), as.numeric) %>% 
  filter(area %in% states$name) %>% 
  pivot_longer(cols=2:ncol(.),
               names_to = "indicator",
               values_to = "value") %>% 
  group_by(indicator) %>% 
  mutate(rank = dense_rank(desc(value))) %>% 
  mutate(indicator = str_replace(indicator,"doses_administered_per_100k_of_65_pop_by_state_where_administered","Administered Per 100k (Age 65+ Where Administered)"),
         indicator = str_replace(indicator,"doses_administered_per_100k_by_state_where_administered","Administered Per 100k (Where Administered)"),
         indicator = str_replace(indicator,"doses_delivered_per_100k_of_65_pop","Delivered Per 100k (Age 65+)"),
         indicator = str_replace(indicator,"doses_delivered_per_100k","Delivered Per 100k"),
         indicator = str_replace(indicator,"percent_of_total_pop_with_at_least_one_dose_by_state_of_residence","At Least 1 Dose (% of Residents)"),         
         indicator = str_replace(indicator,"percent_of_total_pop_fully_vaccinated_by_state_of_residence","Fully Vaccinated (% of Residents)"),
         indicator = str_replace(indicator,"percent_of_total_pop_with_1_doses_by_state_of_residence","With 1 Dose (% of Residents)"),
         indicator = str_replace(indicator,"percent_of_total_pop_with_2_doses_by_state_of_residence","With 2 Doses (% of Residents)"),
         indicator = str_replace(indicator,"percent_of_65_pop_with_at_least_one_dose_by_state_of_residence","At Least 1 Dose (% of Residents Age 65+)"),
         indicator = str_replace(indicator,"percent_of_65_pop_fully_vaccinated_by_state_of_residence","Fully Vaccinated (% of Residents Age 65+)")) %>%
  filter(str_detect(indicator, "Delivered|Administered")) %>% 
  ungroup()

cdc_vaccine_summary_ggplot2 %>% 
  filter(indicator == "Administered Per 100k (Where Administered)") %>%
  ggplot(aes(x=reorder(area, desc(value)), y=value, fill = value)) +
  geom_bar(stat = "identity") +
  geom_point(aes(x=reorder(area, desc(value)), y=value), shape = 21, fill = "#bf5700", color = "black", size = 10, stroke = .1) +
  geom_text(angle=90, color="#ffffff", size = 3.1, family = "LibreFranklin-SemiBold",
            aes(y= 1000, x=area, label = area), hjust = 0) +
  gghighlight(area == "Texas") +
  geom_text(data = cdc_vaccine_summary_ggplot2 %>% filter(indicator == "Administered Per 100k (Where Administered)", area != "Texas"), 
            angle=90, color="#2d2d2d", size = 3.1, family = "LibreFranklin-SemiBold", aes(y= 1000, x=area, label = area), hjust = 0) +
  geom_point(aes(x=reorder(area, desc(value)), y=value), shape = 21, fill = "#bf5700", color = "black", size = 10, stroke = .1) +
  geom_text(data = cdc_vaccine_summary_ggplot2 %>% filter(indicator == "Administered Per 100k (Where Administered)", area == "Texas"), 
            angle=90, color="#ffffff", size = 3.5, family = "LibreFranklin-Bold", aes(y= value, x=area, label = rank)) +  
  geom_text(data = cdc_vaccine_summary_ggplot2 %>% filter(indicator == "Administered Per 100k (Where Administered)", area != "Texas"), 
            angle=90, color="#2d2d2d", size = 3.5, family = "LibreFranklin-Bold", aes(y= value, x=area, label = rank)) +  
  theme_minimal(base_family = "Graphik") +
  theme(plot.title = element_text(family = "Graphik-Bold", color = "#333f48", size =20),
        plot.subtitle = element_text(family = "Graphik-Regular", color = "#333f48", margin = margin(b=15)),
        panel.grid.major.y = element_blank(),
        plot.margin = margin(t=15, r=15, b=10, l = 15),
        axis.text.x = element_blank(),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "none") +
  # theme() +
  scale_y_continuous(label = scales::comma) +
  labs(title = "How Texas Vaccine Administration Stacks Up Against US States + DC", 
       subtitle = paste0("Shown are rankings of vaccine administration, based on the number of doses administered for every 100,000 people\nin a given state. Data is from the CDC. Data reflects reporting as of ",cdc_last_update," at ", cdc_last_time),
       y = "Doses Delivered Per 100k Persons",
       x = "States and DC",
       caption = "Source: 'COVID Data Tracker - Vaccines', Center for Disease Control.")
ggsave(paste0("figures/",today,"_","tx_us_comparison_vaccine_administration.png"), device = "png", dpi = 300, width =11, height = 5)

```

<!-- # Daily Doses Administered -->

<!-- The following charts show data for the daily administration of vaccines across the general population of Texas as well as the different age groups reported by the Texas Department of State Health Services through their Texas Accessible Vaccine Dashboard Data. -->

<!-- ## All Age Groups {.unnumbered} -->

<!-- ## Ages 12-49 years {.unnumbered} -->

<!-- ```{r daily-dose-chart-12, echo=FALSE, layout="l-page"} -->

<!-- library(quantmod) -->

<!-- vaccine_summ_daily <- read_excel(filepath, sheet = 4, skip=0, col_types = c("text", "date", "numeric")) %>%  -->
<!--   clean_names() %>%  -->
<!--   filter(age_group=="12-49 years") %>%  -->
<!--   group_by(date=vaccination_date) %>% -->
<!--   summarise(daily_doses = sum(doses_administered)) %>%  -->
<!--   mutate(date=as.Date(date)) %>%  -->
<!--   mutate(new_doses_7_day_avg= rollmean(daily_doses, 7, fill =0, -->
<!--                                    align = "right")) %>% -->
<!--   mutate(date = as.Date(date, format("%b %d %Y"))) %>%  -->
<!--   ungroup() %>%  -->
<!--   drop_na() -->

<!--   hcoptslang <- getOption("highcharter.lang") -->
<!--   hcoptslang$thousandsSep <- "," -->
<!--   options(highcharter.lang = hcoptslang) -->

<!-- myMenuItems <- c("downloadCSV", "downloadXLS","separator", "downloadPNG", "downloadJPEG", "downloadPDF", "downloadSVG") -->

<!-- highchart(type = "stock") %>%  -->
<!--       hc_add_series(vaccine_summ_daily, type = "column", hcaes(x = date, y = daily_doses), -->
<!--                     tooltip = list(pointFormat = "Daily Doses Administered: {point.daily_doses:,.0f}"), -->
<!--                     color = "#333f48", name="Daily Doses Administered") %>% -->
<!--       hc_add_series(vaccine_summ_daily, type = "area", hcaes(x = date, y = new_doses_7_day_avg), -->
<!--                     tooltip = list(pointFormat = "7-Day Avg.: {point.new_doses_7_day_avg:,.0f}"), -->
<!--                     color = "#bf5700", name="7-Day Avg.") %>%  -->
<!--       hc_plotOptions(area = list(fillOpacity=.1)) %>%  -->
<!--       hc_title( -->
<!--         text ="Daily Administered Doses - 12 to 49 Years", -->
<!--         useHTML = TRUE) %>% -->
<!-- hc_subtitle( -->
<!--         text ="Shown are the number of reported daily administered doses across the state of Texas and the 7-day average of daily adminsitered doses. LEGEND - <span style='color: #bf5700'>7-DAY ROLLING AVG.</span>", -->
<!--         useHTML = TRUE) %>%  -->
<!--       hc_yAxis(title = list(text ="New Doses Administered Per Day", style = list(color = "#333f48", fontSize = "12px",  -->
<!--                                                   color="#333f48",fontWeight="500")), -->
<!--                min = min(vaccine_summ_daily$daily_doses), -->
<!--                max = max(vaccine_summ_daily$daily_doses), -->
<!--                labels =list(style = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif', color="#2d2d2d"))) %>%  -->
<!--       # hc_xAxis(title=NULL, -->
<!--       #          plotLines=plotLines) %>%  -->
<!--       # hc_tooltip(table = TRUE, sort = TRUE, -->
<!--       #            pointFormat = "<b>{point.name}</b><br> -->
<!--       #              New Doses: {point.y:,.0f}") %>%  -->
<!--       hc_legend(enabled=FALSE) %>%  -->
<!--       hc_credits( -->
<!--         enabled = TRUE, -->
<!--         text = "Source: Texas DSHS - COVID-19 Accessible Vaccine Dashboard Data", -->
<!--         href = "https://dshs.texas.gov/immunize/covid19/COVID-19-Vaccine-Data-by-County.xls") %>% -->
<!--       hc_add_theme(lbjdata::hc_theme_lbj()) %>%  -->
<!--       hc_rangeSelector(allButtonsEnabled= FALSE, enabled = TRUE,  -->
<!--                        verticalAlign = "top", -->
<!--                        selected = 3, inputBoxBorderColor= 'white') -->

<!-- ``` -->

<!-- ## Ages 50-64 years {.unlisted} -->

<!-- ```{r daily-dose-chart-50, echo=FALSE, layout="l-page"} -->

<!-- library(quantmod) -->

<!-- vaccine_summ_daily <- read_excel(filepath, sheet = 4, skip=0, col_types = c("text", "date", "numeric")) %>%  -->
<!--   clean_names() %>%  -->
<!--   filter(age_group=="50-64 years") %>%  -->
<!--   group_by(date=vaccination_date) %>% -->
<!--   summarise(daily_doses = sum(doses_administered)) %>%  -->
<!--   mutate(date=as.Date(date)) %>%  -->
<!--   mutate(new_doses_7_day_avg= rollmean(daily_doses, 7, fill =0, -->
<!--                                    align = "right")) %>% -->
<!--   mutate(date = as.Date(date, format("%b %d %Y"))) %>%  -->
<!--   ungroup() %>%  -->
<!--   drop_na() -->

<!--   hcoptslang <- getOption("highcharter.lang") -->
<!--   hcoptslang$thousandsSep <- "," -->
<!--   options(highcharter.lang = hcoptslang) -->

<!-- myMenuItems <- c("downloadCSV", "downloadXLS","separator", "downloadPNG", "downloadJPEG", "downloadPDF", "downloadSVG") -->

<!-- highchart(type = "stock") %>%  -->
<!--       hc_add_series(vaccine_summ_daily, type = "column", hcaes(x = date, y = daily_doses), -->
<!--                     tooltip = list(pointFormat = "Daily Doses Administered: {point.daily_doses:,.0f}"), -->
<!--                     color = "#333f48", name="Daily Doses Administered") %>% -->
<!--       hc_add_series(vaccine_summ_daily, type = "area", hcaes(x = date, y = new_doses_7_day_avg), -->
<!--                     tooltip = list(pointFormat = "7-Day Avg.: {point.new_doses_7_day_avg:,.0f}"), -->
<!--                     color = "#bf5700", name="7-Day Avg.") %>%  -->
<!--       hc_plotOptions(area = list(fillOpacity=.1)) %>%  -->
<!--       hc_title( -->
<!--         text ="Daily Administered Doses - 50 to 64 years", -->
<!--         useHTML = TRUE) %>% -->
<!-- hc_subtitle( -->
<!--         text ="Shown are the number of reported daily administered doses across the state of Texas and the 7-day average of daily adminsitered doses. LEGEND - <span style='color: #bf5700'>7-DAY ROLLING AVG.</span>", -->
<!--         useHTML = TRUE) %>%  -->
<!--       hc_yAxis(title = list(text ="New Doses Administered Per Day", style = list(color = "#333f48", fontSize = "12px",  -->
<!--                                                   color="#333f48",fontWeight="500")), -->
<!--                min = min(vaccine_summ_daily$daily_doses), -->
<!--                max = max(vaccine_summ_daily$daily_doses), -->
<!--                labels =list(style = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif', color="#2d2d2d"))) %>%  -->
<!--       # hc_xAxis(title=NULL, -->
<!--       #          plotLines=plotLines) %>%  -->
<!--       # hc_tooltip(table = TRUE, sort = TRUE, -->
<!--       #            pointFormat = "<b>{point.name}</b><br> -->
<!--       #              New Doses: {point.y:,.0f}") %>%  -->
<!--       hc_legend(enabled=FALSE) %>%  -->
<!--       hc_credits( -->
<!--         enabled = TRUE, -->
<!--         text = "Source: Texas DSHS - COVID-19 Accessible Vaccine Dashboard Data", -->
<!--         href = "https://dshs.texas.gov/immunize/covid19/COVID-19-Vaccine-Data-by-County.xls") %>% -->
<!--       hc_add_theme(lbjdata::hc_theme_lbj()) %>%  -->
<!--       hc_rangeSelector(allButtonsEnabled= FALSE, enabled = TRUE,  -->
<!--                        verticalAlign = "top", -->
<!--                        selected = 3, inputBoxBorderColor= 'white') -->

<!-- ``` -->

<!-- ## Ages 65-79 years {.unlisted} -->

<!-- ```{r daily-dose-chart-65, echo=FALSE, layout="l-page"} -->

<!-- library(quantmod) -->

<!-- vaccine_summ_daily <- read_excel(filepath, sheet = 4, skip=0, col_types = c("text", "date", "numeric")) %>%  -->
<!--   clean_names() %>%  -->
<!--   filter(age_group=="65-79 years") %>%  -->
<!--   group_by(date=vaccination_date) %>% -->
<!--   summarise(daily_doses = sum(doses_administered)) %>%  -->
<!--   mutate(date=as.Date(date)) %>%  -->
<!--   mutate(new_doses_7_day_avg= rollmean(daily_doses, 7, fill =0, -->
<!--                                    align = "right")) %>% -->
<!--   mutate(date = as.Date(date, format("%b %d %Y"))) %>%  -->
<!--   ungroup() %>%  -->
<!--   drop_na() -->

<!--   hcoptslang <- getOption("highcharter.lang") -->
<!--   hcoptslang$thousandsSep <- "," -->
<!--   options(highcharter.lang = hcoptslang) -->

<!-- myMenuItems <- c("downloadCSV", "downloadXLS","separator", "downloadPNG", "downloadJPEG", "downloadPDF", "downloadSVG") -->

<!-- highchart(type = "stock") %>%  -->
<!--       hc_add_series(vaccine_summ_daily, type = "column", hcaes(x = date, y = daily_doses), -->
<!--                     tooltip = list(pointFormat = "Daily Doses Administered: {point.daily_doses:,.0f}"), -->
<!--                     color = "#333f48", name="Daily Doses Administered") %>% -->
<!--       hc_add_series(vaccine_summ_daily, type = "area", hcaes(x = date, y = new_doses_7_day_avg), -->
<!--                     tooltip = list(pointFormat = "7-Day Avg.: {point.new_doses_7_day_avg:,.0f}"), -->
<!--                     color = "#bf5700", name="7-Day Avg.") %>%  -->
<!--       hc_plotOptions(area = list(fillOpacity=.1)) %>%  -->
<!--       hc_title( -->
<!--         text ="Daily Administered Doses - 65 to 79", -->
<!--         useHTML = TRUE) %>% -->
<!-- hc_subtitle( -->
<!--         text ="Shown are the number of reported daily administered doses across the state of Texas and the 7-day average of daily adminsitered doses. LEGEND - <span style='color: #bf5700'>7-DAY ROLLING AVG.</span>", -->
<!--         useHTML = TRUE) %>%  -->
<!--       hc_yAxis(title = list(text ="New Doses Administered Per Day", style = list(color = "#333f48", fontSize = "12px",  -->
<!--                                                   color="#333f48",fontWeight="500")), -->
<!--                min = min(vaccine_summ_daily$daily_doses), -->
<!--                max = max(vaccine_summ_daily$daily_doses), -->
<!--                labels =list(style = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif', color="#2d2d2d"))) %>%  -->
<!--       # hc_xAxis(title=NULL, -->
<!--       #          plotLines=plotLines) %>%  -->
<!--       # hc_tooltip(table = TRUE, sort = TRUE, -->
<!--       #            pointFormat = "<b>{point.name}</b><br> -->
<!--       #              New Doses: {point.y:,.0f}") %>%  -->
<!--       hc_legend(enabled=FALSE) %>%  -->
<!--       hc_credits( -->
<!--         enabled = TRUE, -->
<!--         text = "Source: Texas DSHS - COVID-19 Accessible Vaccine Dashboard Data", -->
<!--         href = "https://dshs.texas.gov/immunize/covid19/COVID-19-Vaccine-Data-by-County.xls") %>% -->
<!--       hc_add_theme(lbjdata::hc_theme_lbj()) %>%  -->
<!--       hc_rangeSelector(allButtonsEnabled= FALSE, enabled = TRUE,  -->
<!--                        verticalAlign = "top", -->
<!--                        selected = 3, inputBoxBorderColor= 'white') -->

<!-- ``` -->

<!-- ## Ages 80 years or older {.unlisted} -->

<!-- ```{r daily-dose-chart-80, echo=FALSE, layout="l-page"} -->

<!-- library(quantmod) -->

<!-- vaccine_summ_daily <- read_excel(filepath, sheet = 4, skip=0, col_types = c("text", "date", "numeric")) %>%  -->
<!--   clean_names() %>%  -->
<!--   filter(age_group=="80+ years") %>%  -->
<!--   group_by(date=vaccination_date) %>% -->
<!--   summarise(daily_doses = sum(doses_administered)) %>%  -->
<!--   mutate(date=as.Date(date)) %>%  -->
<!--   mutate(new_doses_7_day_avg= rollmean(daily_doses, 7, fill =0, -->
<!--                                    align = "right")) %>% -->
<!--   mutate(date = as.Date(date, format("%b %d %Y"))) %>%  -->
<!--   ungroup() %>%  -->
<!--   drop_na() -->

<!--   hcoptslang <- getOption("highcharter.lang") -->
<!--   hcoptslang$thousandsSep <- "," -->
<!--   options(highcharter.lang = hcoptslang) -->

<!-- myMenuItems <- c("downloadCSV", "downloadXLS","separator", "downloadPNG", "downloadJPEG", "downloadPDF", "downloadSVG") -->

<!-- highchart(type = "stock") %>%  -->
<!--       hc_add_series(vaccine_summ_daily, type = "column", hcaes(x = date, y = daily_doses), -->
<!--                     tooltip = list(pointFormat = "Daily Doses Administered: {point.daily_doses:,.0f}"), -->
<!--                     color = "#333f48", name="Daily Doses Administered") %>% -->
<!--       hc_add_series(vaccine_summ_daily, type = "area", hcaes(x = date, y = new_doses_7_day_avg), -->
<!--                     tooltip = list(pointFormat = "7-Day Avg.: {point.new_doses_7_day_avg:,.0f}"), -->
<!--                     color = "#bf5700", name="7-Day Avg.") %>%  -->
<!--       hc_plotOptions(area = list(fillOpacity=.1)) %>%  -->
<!--       hc_title( -->
<!--         text ="Daily Administered Doses - 80 years or older", -->
<!--         useHTML = TRUE) %>% -->
<!-- hc_subtitle( -->
<!--         text ="Shown are the number of reported daily administered doses across the state of Texas and the 7-day average of daily adminsitered doses. LEGEND - <span style='color: #bf5700'>7-DAY ROLLING AVG.</span>", -->
<!--         useHTML = TRUE) %>%  -->
<!--       hc_yAxis(title = list(text ="New Doses Administered Per Day", style = list(color = "#333f48", fontSize = "12px",  -->
<!--                                                   color="#333f48",fontWeight="500")), -->
<!--                min = min(vaccine_summ_daily$daily_doses), -->
<!--                max = max(vaccine_summ_daily$daily_doses), -->
<!--                labels =list(style = list(fontFamily = '"Libre Franklin", -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, "Helvetica Neue", Arial, sans-serif', color="#2d2d2d"))) %>%  -->
<!--       # hc_xAxis(title=NULL, -->
<!--       #          plotLines=plotLines) %>%  -->
<!--       # hc_tooltip(table = TRUE, sort = TRUE, -->
<!--       #            pointFormat = "<b>{point.name}</b><br> -->
<!--       #              New Doses: {point.y:,.0f}") %>%  -->
<!--       hc_legend(enabled=FALSE) %>%  -->
<!--       hc_credits( -->
<!--         enabled = TRUE, -->
<!--         text = "Source: Texas DSHS - COVID-19 Accessible Vaccine Dashboard Data", -->
<!--         href = "https://dshs.texas.gov/immunize/covid19/COVID-19-Vaccine-Data-by-County.xls") %>% -->
<!--       hc_add_theme(lbjdata::hc_theme_lbj()) %>%  -->
<!--       hc_rangeSelector(allButtonsEnabled= FALSE, enabled = TRUE,  -->
<!--                        verticalAlign = "top", -->
<!--                        selected = 3, inputBoxBorderColor= 'white') -->

<!-- ``` -->

<!-- # Vaccine Hesitancy -->

<!-- Recently, the U.S. Department of Health and Human Services began publishing predicted estimates for vaccine hesitancy across the United States across different geographies in the US.  -->

```{r eval=FALSE, include=FALSE}
library(mapview)

vax_hesitancy <- RSocrata::read.socrata("https://data.cdc.gov/resource/djj9-kh3p.csv")

```


# Distribution Trends

The next chart captures where the reported supply of doses has been distributed, by the type of vaccine provider. The state classifies provider types, which allows to see very simply: what kinds of providers have recently received shipments of doses and how much were they shipped?

**Note as of Mar 31**: The chart showing how much DSHS has shipped to each provider type across Texas has been temporarily removed due to the fact that DSHS appears to have stopped publishing a column showing how much was shipped to each provider in their daily updates of the ["Texas Vaccine Provider Data"](https://genesis.soc.texas.gov/files/accessibility/vaccineprovideraccessibilitydata.csv).

```{r eval=FALSE, fig.width=10, include=FALSE, layout="l-page"}

supply_by_provider_type <- read_csv(filepath_providers, skip=0) %>%
  janitor::clean_names() %>% 
  group_by(type) %>% 
  summarise(tot_shipped = sum(total_shipped),
            tot_avail = sum(vaccines_available)) 

supply_by_provider_type %>%
  drop_na() %>%
  ggplot(aes(x=reorder(type, desc(tot_shipped)), y = tot_shipped, fill=type)) +
  geom_col() +
  theme_minimal(base_family = "Graphik") +
  geom_text(angle=90, color="#2d2d2d", size = 3.1, family = "Graphik-Semibold",
            aes(y= 0, x=type, label = type), hjust = 0) +
  scale_y_continuous(labels = scales::unit_format(unit = "K", accuracy = 1, scale = 1e-3)) +
  ggthemes::scale_fill_tableau(palette = "Tableau 20") +
  theme(plot.title = element_text(family = "Graphik-Bold", color = "#333f48", size =20),
        plot.subtitle = element_text(family = "Graphik-Regular", color = "#333f48", margin = margin(b=15)),
        panel.grid.major.y = element_blank(),
        plot.margin = margin(t=15, r=15, b=10, l = 15),
        axis.text.x = element_blank(),
        legend.position = "none") +
  labs(title = "Reported Total Supply by Provider Type",
       subtitle = paste0("Source: Texas Department of State Health Services. Last pulled on ", today_lbl, " at ", time_lbl),
       x = NULL,
       y = "Doses (Shipped)",
       color = NULL,
       caption = "Data File: 'Texas Vaccine Provider Data'\nLink: https://genesis.soc.texas.gov/files/accessibility/vaccineprovideraccessibilitydata.csv\nChart by: @mrworthington") #+
  # ggsave(paste0("figures/",today,"_","supply_by_provider_type.png"), dpi = 300, width = 11, height = 4.5)

```

Similar to the last one, this chart focuses on reported availability. In other words, how much of the shipped doses are provider types reporting to be still available at the time the chart was generated? 

```{r echo=FALSE, fig.width=10, layout="l-page"}

supply_by_provider_type <- read_csv(filepath_providers, skip=0) %>%
  janitor::clean_names() %>% 
  group_by(type) %>% 
  summarise(tot_avail = sum(vaccines_available)) 

supply_by_provider_type %>% 
  drop_na() %>% 
  ggplot(aes(x=reorder(type, desc(tot_avail)), y = tot_avail, fill=type)) +
  geom_col() +
  theme_minimal(base_family = "Graphik") +
  geom_text(angle=90, color="#2d2d2d", size = 3.1, family = "Graphik-Semibold",
            aes(y= 0, x=type, label = type), hjust = 0) +
  scale_y_continuous(labels = scales::unit_format(unit = "K", accuracy = 1, scale = 1e-3)) +
  ggthemes::scale_fill_tableau(palette = "Tableau 20") +
  theme(plot.title = element_text(family = "Graphik-Bold", color = "#333f48", size =20),
        plot.subtitle = element_text(family = "Graphik-Regular", color = "#333f48", margin = margin(b=15)),
        panel.grid.major.y = element_blank(),
        plot.margin = margin(t=15, r=15, b=10, l = 15),
        axis.text.x = element_blank(),
        legend.position = "none") +
  labs(title = "Reported Availability by Provider Type",
       subtitle = paste0("Source: Texas Department of State Health Services. Last pulled on ", today_lbl, " at ", time_lbl),
       x = NULL,
       y = "Doses (Available)",
       color = NULL,
       caption = "Data File: 'Texas Vaccine Provider Data'\nLink: https://genesis.soc.texas.gov/files/accessibility/vaccineprovideraccessibilitydata.csv\nChart by: @mrworthington") #+
  # ggsave(paste0("figures/",today,"_","availability_by_provider_type.png"), dpi = 300, width = 11, height = 4.5)
```

<!-- <details class = "l-body"> -->
<!-- <summary><strong>Notes about the table below</strong></summary> -->

<!-- * Data shown below comes from the "Accessible Vaccine Dashboard Data" published by the Texas Department of State Health Services, which can be found at this link: `r src` -->
<!-- * It was last pulled on `r today_lbl` at `r time_lbl` -->

<!-- </details> -->

<!-- <details class = "l-body"> -->
<!-- <summary><strong> Data dictionary for the table below </strong></summary> -->

<!-- * **County**: This comes from the DSHS "Accessible Vaccine Dashboard Data" file and represents the county for which DSHS has collected data. -->
<!-- * **Popuplation (12+)"**:  This comes from the DSHS "Accessible Vaccine Dashboard Data" file and represents the number of persons aged 12 years and older in Texas. This number is reported given that vaccines authorized for emergency use have only authorized for use in persons aged 12 years and older.  -->
<!-- * **Total Doses Allocated**: This comes from the DSHS "Accessible Vaccine Dashboard Data" file and represents the number of total doses allocated/shipped to a given Texas county. -->
<!-- * **Full Vaccinations**: This comes from the DSHS "Accessible Vaccine Dashboard Data" file and represents the number of persons who are fully vaccinated in a given Texas county. -->
<!-- * **Doses Allocated (Per Capita)**: This is a custom calculation that is derived by taking the number of total doses allocated and dividing it by the population aged 12 years and older, both numbers provided by DSHS. The result of that is then multipled by 100,000 for standardization and rounded up.   -->
<!-- * **Full Vaccinations (Per Capita)**: This is a custom calculation that is derived by taking the number of persons who are fully vaccinated and dividing it by the population aged 12 years and older, both numbers provided by DSHS. The result of that is then multipled by 100,000 for standardization and rounded up.   -->

<!-- </details> -->

<!-- ## Vaccine Data Table  -->

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, layout="l-screen-inset"}

vaccine_cnty_summ <- read_excel(filepath, sheet = "By County", skip=0) %>% 
  clean_names() %>% 
  filter(county_name!="Texas" & county_name!="Federal Long-Term Care Vaccination Program" & county_name!="*Other") %>% 
  select(county_name, population_16, people_fully_vaccinated, total_doses_allocated) %>% 
  mutate(population_16 = as.numeric(population_16), 
         people_fully_vaccinated = as.numeric(people_fully_vaccinated), 
         total_doses_allocated = as.numeric(total_doses_allocated)) %>% 
  mutate(doses_allocated_per_cap = round((total_doses_allocated/population_16)*100000, digits=0),
         fully_vaccinated_per_cap = round((people_fully_vaccinated/population_16)*100000, digits=0)) %>% 
  select(county_name, population_16, total_doses_allocated, doses_allocated_per_cap, people_fully_vaccinated, fully_vaccinated_per_cap) %>%   
  arrange(desc(population_16))

reactable(data =vaccine_cnty_summ,
            searchable = TRUE,
            striped = TRUE,
            highlight = TRUE,
            bordered = TRUE,
            pagination = TRUE,
            showSortIcon = TRUE ,
            defaultPageSize = 15,
            resizable = TRUE,
            fullWidth = TRUE,
            compact = TRUE,
            theme = reactableTheme(
              color = "#2d2d2d",
              backgroundColor = "rgba(255,255,255,1)",
              borderColor = "rgba(255,255,255,.2)",
              headerStyle = list(background = "#333f48", 
                                 color = "#fff",
                                 fontWeight="700", 
                                 letterSpacing="1px", 
                                 fontSize="15px"),
              highlightColor = "#9cadb7",
              cellPadding = "8px 12px",
              style = list(fontSize = "14px",
                           fontFamily = "'Libre Franklin', -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"),
              searchInputStyle = list(width = "100%")),
          columns = list(
            county_name = colDef(name = "County", show = TRUE, width = 110,
                                 style = list(borderRight = "1px solid rgba(0, 0, 0, 0.1)")),
            population_16 = colDef(show = TRUE, width = 180,
                                   header = with_tooltip("Population (12+)", "Number of Persons"),
                                   format = colFormat(separators = TRUE),
                                   align = "center",
                                   style = list(borderRight = "1.5px solid rgba(0, 0, 0, 0.2)")),
            total_doses_allocated = colDef(show = TRUE, format = colFormat(separators = TRUE),
                                           align = "center", 
                                           width = 250,
                                           header = with_tooltip("Total Doses Allocated", "Number of Doses Allocated")),
            doses_allocated_per_cap = colDef(show = TRUE,
                                             header = with_tooltip("Doses Allocated (Per Capita)", "For every 100,000 persons, how many doses have been allocated to this county?"),
                                             style = list(borderRight = "1.5px solid rgba(0, 0, 0, 0.2)", fontFamily = "Fira Code", whiteSpace = "pre"),
                                             align = "left",
                                             cell = function(value) {
                                                       width <- paste0(value * 100 / max(vaccine_cnty_summ$doses_allocated_per_cap, na.rm = TRUE), "%")
                                                       # Add thousands separators
                                                       value <- format(value, big.mark = ",")
                                                       # Fix each label using the width of the widest number (incl. thousands separators)
                                                       value <- format(value, width = 9, justify = "right")
                                                       bar_chart(value, width = width, fill = "#bf5700")
                                             }),
            people_fully_vaccinated = colDef(show = TRUE,  
                                             format = colFormat(separators = TRUE),
                                             align = "center", 
                                             width = 250,
                                             header = with_tooltip("Full Vaccinations", "Number of Persons")),
            fully_vaccinated_per_cap = colDef(show = TRUE,
                                              header = with_tooltip("Full Vaccinations (Per Capita)", "For every 100,000 persons, how many would be fully vaccinated?"),
                                             style = list(borderRight = "1.5px solid rgba(0, 0, 0, 0.2)", fontFamily = "Fira Code", whiteSpace = "pre"),
                                              align = "left",
                                              cell = function(value) {
                                               width <- paste0(value * 100 / max(vaccine_cnty_summ$fully_vaccinated_per_cap, na.rm = TRUE), "%")
                                               value <- format(value, big.mark = ",")
                                               # Fix each label using the width of the widest number (incl. thousands separators)
                                               value <- format(value, width = 9, justify = "right")                                              
                                               bar_chart(value, width = width)
                                             })))

```


+
# Vaccine Pace Tracker

The last tool to track the pace of distribution is an interactive comparison of the state and counties across Texas. The tool allows users to track the statewide pace of vaccine progress and the county-level pace of vaccine progress. Because the state is only focused on the population aged 12 and above, we only measure progress against this population. 

<details class = "l-body">
<summary><strong>Question  | </strong>Why do they only measure the population aged 12 and above?</summary>

<br>
According to [the Texas Department of State Health Services](https://dshs.texas.gov/coronavirus/immunize/vaccine-faqs.aspx#safety), "At this time, experts do not know how safe the COVID-19 vaccine is for children. People 12 years old and older are currently eligible to get the vaccine if they are in a priority population."

</details>

The two charts represent the entire populations of the state and selected county. In the boxes below, there are three indicators. 

1. **Dose Distribution**: This box shows how many doses have been administered out of the doses that have actually been allocated to that entity (either the state or the selected county).
1. **Daily Average**: This is an ongoing calculation of daily averages that starts on Dec 15. The only thing it considers is how many doses are going into arms each day. 
1. **When 70% is Vaccinated**: Based on that daily average and knowing most of the approved vaccines require two doses, this box tries to guesstimate when 70% of the population aged 12 and older will be vaccinated. This is not a herd immunity projection, rather a look ahead as to when most of the population aged 12 and older will likely be vaccinated. 


```{r echo=FALSE, message=FALSE, warning=FALSE, layout = "l-page"}
knitr::include_app("https://mrworthington.shinyapps.io/tx_vaccine-pace/", height = "1800px")
```

## Photography Credit {.appendix}

<span>Photo by <a href="https://unsplash.com/@cdc?utm_source=unsplash&amp;utm_medium=referral&amp;utm_content=creditCopyText">CDC</a> on <a href="https://unsplash.com/?utm_source=unsplash&amp;utm_medium=referral&amp;utm_content=creditCopyText">Unsplash</a></span>
