---
title: "Explore Providers"
description: |
  Which providers are offering the vaccine closest to you? 
output: 
  distill::distill_article:
    toc: true
    css: provider_header.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r eval=FALSE, fig.width=11, include=FALSE, layout="l-page"}

library(gt)
library(tidyverse)
library(ggforce)
library(readxl)
library(janitor)

today <- Sys.Date()
src <- "https://dshs.texas.gov/immunize/covid19/COVID-19-Vaccine-Data-by-County.xls" # URL For Daily COVID Data
lcl <- basename(src)
filepath <- paste0(today,"_",lcl,"x")
download.file(url = src, destfile = filepath) # Downloads The Data
today_lbl <- format(Sys.Date(), format = "%b %d, %Y")
# today_lbl <- format(Sys.Date(), format = "%b %d, %Y")
time_lbl <- format(Sys.time(), format = "%I:%M %p")

vaccine_summ <- read_excel(filepath, sheet = "By County", skip=0) %>% 
  clean_names() %>% 
  filter(county_name=="Texas") %>% 
  mutate(across(total_doses_allocated:population_phase_1b_any_medical_condition, as.numeric)) %>%
  select(county_name, population_16, people_fully_vaccinated, total_doses_allocated, starts_with("population_phase_")) %>% 
  mutate(population_phase_remaining = population_16 - (population_phase_1a_healthcare_workers +
                                                       population_phase_1a_long_term_care_residents +
                                                       population_phase_1b_any_medical_condition),
         remaining_box_start = population_16 - population_phase_remaining) %>%
  rename(`Phase 1A - Healthcare Workers`=population_phase_1a_healthcare_workers, 
         `Phase 1A - Long Term Care`=population_phase_1a_long_term_care_residents, 
         `Phase 1B - 65+ and High Risk`=population_phase_1b_any_medical_condition,
         `Future Phases`=population_phase_remaining) %>%
  pivot_longer(cols=contains("Phase"), names_to = "phase_pop_est", values_to = "value") %>%
  mutate(order = case_when(
    phase_pop_est == "Phase 1A - Healthcare Workers" ~ 1,
    phase_pop_est == "Phase 1A - Long Term Care" ~ 2,
    phase_pop_est == "Phase 1B - 65+ and High Risk" ~ 3,
  ),
  prev_1 = lag(value, 1),
  prev_2 = lag(value, 2),
  prev_1 = replace_na(prev_1, 0),
  prev_2 = replace_na(prev_2, 0)) %>% 
  mutate(lab_pos = (value/2) + (prev_1 + prev_2)) 

box_start <- unique(vaccine_summ$remaining_box_start)
box_end <- unique(vaccine_summ$population_16)
fully_vac_lbl <- scales::comma(unique(vaccine_summ$people_fully_vaccinated))
shipped_lbl <- scales::comma(unique(vaccine_summ$total_doses_allocated))

vaccine_summ %>%
  ggplot() +
  geom_col(data = . %>%  slice(1), aes(y=county_name, x=population_16), fill = "#333f48", alpha = .05) +
  geom_col(data = vaccine_summ %>% filter(phase_pop_est != "Future Phases"), aes(y=county_name, x=value, fill = reorder(phase_pop_est,desc(order))), alpha=.7) +
  annotate(geom = "rect", alpha = 0, color = "#333f48", linetype = 2, 
           xmin = box_start, xmax = box_end, ymin = .55, ymax = 1.45) +
  geom_text(data = . %>% filter(phase_pop_est != "Future Phases"), angle=90, color="white", size = 3.1, family = "Graphik-Semibold",
            aes(y=county_name, x=lab_pos, label = reorder(phase_pop_est,desc(order)))) +
  geom_text(data = vaccine_summ %>% filter(phase_pop_est == "Future Phases"), color="#2d2d2d", size = 6,  hjust = 0.35,
            family = "Graphik-Semibold", aes(y=county_name, x=lab_pos), label = "Remaining Pop. (16+) in Future Phases") +
  geom_vline(aes(xintercept=total_doses_allocated), linetype = 2, size = .9, color = "#2d2d2d") +
  geom_vline(aes(xintercept=people_fully_vaccinated), linetype = 2, size = .9, color = "#2d2d2d") +
  scale_x_continuous(labels = scales::unit_format(unit = "M", accuracy = 1, scale = 1e-6)) +
  scale_fill_manual(values = c("#005f86",  "#9cadb7","#bf5700")) +
  guides(fill=guide_legend(title = "Legend",
                           keyheight = .8)) +
  annotate(
    geom = "curve", color = "#2d2d2d", x = 4158050, y = 1.55, xend = 3458050, yend = 1.5,
    curvature = .1, arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(geom = "label", x = 4158050, y = 1.53, color = "#2d2d2d", 
           label = glue::glue("Doses Shipped: {shipped_lbl}"), family = "Graphik", hjust = "left") +
  annotate(
    geom = "curve", color = "#2d2d2d", x = 902396, y = .48, xend = 302396, yend = .54 , 
    curvature = -.1, arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(geom = "label", x = 902396, y = .5, color = "#2d2d2d", 
           label = glue::glue("Persons Fully Vacinated: {fully_vac_lbl}"), family = "Graphik", hjust = "left") +
  theme_minimal(base_family = "Graphik") +
  theme(plot.title = element_text(family = "Graphik-Bold", color = "#333f48", size =20),
        plot.subtitle = element_text(family = "Graphik-Regular", color = "#333f48", margin = margin(b=15)),
        panel.grid.major.y = element_blank(),
        plot.margin = margin(t=15, r=15, b=10, l = 15),
        axis.text.y = element_blank(),
        legend.position = "none") +
  labs(title = "Texas Summary of Vaccination Progress",
       subtitle = paste0("Source: Texas Department of State Health Services. As of ", today_lbl, " at ", time_lbl),
       x = NULL,
       y = NULL,
       color = NULL,
       caption = "Data File: 'Accessible Vaccine Dashboard Data'\nLink: https://dshs.texas.gov/immunize/covid19/COVID-19-Vaccine-Data-by-County.xls\nChart by: @mrworthington") #+
  # ggsave(paste0(today,"_","tx_vaccine_summary.png"), dpi = 300, width = 11, height = 4.5)

```

```{r eval=FALSE, include=FALSE}
today <- Sys.Date()
src <- "https://genesis.soc.texas.gov/files/accessibility/vaccineprovideraccessibilitydata.csv"
lcl <- basename(src)
filepath <- paste0(today,"_",lcl)
download.file(url = src, destfile = filepath)

# provider_locations <- read_rds("clean_data/vaccine_supply_by_site.rds") %>%
  # select(name, street, lat, lon)

supply_by_provider_type <- read_csv(filepath, skip=0) %>%
  janitor::clean_names() %>% 
  group_by(type) %>% 
  summarise(tot_shipped = sum(total_shipped),
            tot_avail = sum(total_available)) 

supply_by_provider_type %>% 
  drop_na() %>% 
  ggplot(aes(x=reorder(type, desc(tot_shipped)), y = tot_shipped, fill=type)) +
  geom_col() +
  theme_minimal(base_family = "Graphik") +
  geom_text(angle=90, color="#2d2d2d", size = 3.1, family = "Graphik-Semibold",
            aes(y= 0, x=type, label = type), hjust = 0) +
  scale_y_continuous(labels = scales::unit_format(unit = "K", accuracy = 1, scale = 1e-3)) +
  ggthemes::scale_fill_tableau(palette = "Tableau 20") +
  theme(plot.title = element_text(family = "Graphik-Bold", color = "#333f48", size =20),
        plot.subtitle = element_text(family = "Graphik-Regular", color = "#333f48", margin = margin(b=15)),
        panel.grid.major.y = element_blank(),
        plot.margin = margin(t=15, r=15, b=10, l = 15),
        axis.text.x = element_blank(),
        legend.position = "none") +
  labs(title = "Reported Total Supply by Provider Type",
       subtitle = paste0("Source: Texas Department of State Health Services. As of ", today_lbl, " at ", time_lbl),
       x = NULL,
       y = "Doses (Shipped)",
       color = NULL,
       caption = "Data File: 'Texas Vaccine Provider Data'\nLink: https://genesis.soc.texas.gov/files/accessibility/vaccineprovideraccessibilitydata.csv\nChart by: @mrworthington") +
  ggsave(paste0(today,"_","supply_by_provider_type.png"), dpi = 300, width = 11, height = 4.5)

supply_by_provider_type %>% 
  drop_na() %>% 
  ggplot(aes(x=reorder(type, desc(tot_avail)), y = tot_avail, fill=type)) +
  geom_col() +
  theme_minimal(base_family = "Graphik") +
  geom_text(angle=90, color="#2d2d2d", size = 3.1, family = "Graphik-Semibold",
            aes(y= 0, x=type, label = type), hjust = 0) +
  scale_y_continuous(labels = scales::unit_format(unit = "K", accuracy = 1, scale = 1e-3)) +
  ggthemes::scale_fill_tableau(palette = "Tableau 20") +
  theme(plot.title = element_text(family = "Graphik-Bold", color = "#333f48", size =20),
        plot.subtitle = element_text(family = "Graphik-Regular", color = "#333f48", margin = margin(b=15)),
        panel.grid.major.y = element_blank(),
        plot.margin = margin(t=15, r=15, b=10, l = 15),
        axis.text.x = element_blank(),
        legend.position = "none") +
  labs(title = "Reported Availability by Provider Type",
       subtitle = paste0("Source: Texas Department of State Health Services. As of ", today_lbl, " at ", time_lbl),
       x = NULL,
       y = "Doses (Available)",
       color = NULL,
       caption = "Data File: 'Texas Vaccine Provider Data'\nLink: https://genesis.soc.texas.gov/files/accessibility/vaccineprovideraccessibilitydata.csv\nChart by: @mrworthington") +
  ggsave(paste0(today,"_","availability_by_provider_type.png"), dpi = 300, width = 11, height = 4.5)
```


## Eligible Populations

Right now, the state has highlighted two phases of the Texas Population that are eligible to receive available COVID-19 vaccines: Phase 1A and Phase 1B. To learn more about each of the populations, expand the summaries below.

<details class = "l-body">
<summary><strong>Eligible Population | </strong>Phase 1A</summary>

\newline

Below is a description of the Phase 1A population, as described by the Texas Department of State Health Services.

## Phase 1A {.unlisted .unnumbered}

### First Tier

* Paid and unpaid workers in hospital settings working directly with patients wh* are positive or at high risk for COVID-19. Such as but not limited to:
* Physicians, nurses, respiratory therapists and other support staff (custodial staff, etc.)
* Additional clinical staff providing supporting laboratory, pharmacy, diagnostic and/or rehabilitation services
* Others having direct contact with patients or infectious materials
* Long-term care staff working directly with vulnerable residents. Includes:
* Direct care providers at nursing homes, assisted living facilities, and state supported living centers
* Physicians, nurses, personal care assistants, custodial, food service staff
* EMS providers wh* engage in 9-1-1 emergency services like pre-hospital care and
transport
* Home health care workers, including hospice care, wh* directly interface with
vulnerable and high-risk patients
* Residents of long-term care facilities

### Second Tier

* Staff in outpatient care settings wh* interact with symptomatic patients. Such as but not limited to:
* Physicians, nurses, and other support staff (custodial staff, etc.)
* Clinical staff providing diagnostic, laboratory, and/or rehabilitation services * Non 9-1-1 transport for routine care
* Healthcare workers in corrections and detention facilities
* Direct care staff in freestanding emergency medical care facilities and urgent care clinics
* Community pharmacy staff wh* may provide direct services t* clients, including
vaccination or testing for individuals wh* may have COVID
* Public health and emergency response staff directly involved in administration of COVID
testing and vaccinations
* Last responders wh* provide mortuary or death services t* decedents with COVID-19.
Includes:
* Embalmers and funeral home workers wh* have direct contact with decedents * Medical examiners and other medical certifiers wh* have direct contact with
decedents
* School nurses wh* provide health care t* students and teachers

```{r eval=FALSE, include=FALSE}

library(gt)
library(tidyverse)
library(readxl)
library(janitor)

today <- Sys.Date()
src <- "https://dshs.texas.gov/immunize/covid19/COVID-19-Vaccine-Data-by-County.xls" # URL For Daily COVID Data
lcl <- basename(src)
filepath <- paste0(today,"_",lcl,"x")
download.file(url = src, destfile = filepath) # Downloads The Data

read_excel(filepath, sheet = "By County", skip=0) %>% 
  clean_names() %>% 
  select(county_name, total_doses_allocated, vaccine_doses_administered) %>% 
  mutate(total_doses_allocated = as.numeric(total_doses_allocated),
         vaccine_doses_administered = as.numeric(vaccine_doses_administered)) %>% 
  filter(county_name=="Texas") %>% 
  pivot_longer(cols=c(total_doses_allocated, vaccine_doses_administered), names_to = "type", values_to = "value") %>% 
  gt() %>% 
  tab_header(title = md("**Phase 1B Eligibility**"),
             subtitle = "Source: Texas Department of State Health Services | As of January 10th at 3:00PM CST") %>%
  tab_source_note(
    source_note = "*Unable to deduplicate figures for Commercial labs."
  ) %>% 
  tab_footnote(footnote = md("[Data: From the 'Accessible Dashboard Data' File, under the 'Tests' tab.](https://www.dshs.state.tx.us/coronavirus/additionaldata/)"), locations = cells_title("subtitle")) %>% 
    fmt_number(columns="value", suffixing=TRUE) %>% 
  cols_label(county_name=md("**Location**"),
             type=md("**Type**"),
             value=md("**Value**")) %>% 
  tab_options(
    grand_summary_row.background.color = "#f5f5f5",
    heading.title.font.weight = "800",
  )
```

</details>

<details class = "l-body">
<summary><strong>Eligible Population  | </strong>Phase 1B</summary>

\newline

Below is a description of the Phase 1B population, as described by the Texas Department of State Health Services.

## Phase 1B {.unlisted .unnumbered}

* People 65 years of age and older
* People 16 years of age and older with at least one chronic medical condition that puts
them at increased risk for severe illness from the virus that causes COVID-19, such as but not limited to:
* Cancer
* Chronic kidney disease
* COPD (chronic obstructive pulmonary disease)
* Heart conditions, such as heart failure, coronary artery disease or cardiomyopathies
* Solid organ transplantation
* Obesity and severe obesity (body mass index of 30 kg/m2 or higher)
* Pregnancy
* Sickle cell disease
* Type 2 diabetes mellitus

</details>

## Vaccine Providers

The tool below is a resource designed to help you find a vaccine provider in your county that has recently reported having availability. To learn more about whether or not you are currently eligible, please read the "Eligible Populations" section above. Enter a zip code, city, county, or complete address[^1] to see the latest data on providers in your county.

[^1]: A street address should contain a Street Number, Street Name, and a city. Unit and/or apartment numbers are not needed.

```{r echo=FALSE, message=FALSE, warning=FALSE, layout = "l-screen-inset"}
knitr::include_app("https://mrworthington.shinyapps.io/tx_vaccine-explorer/", height = "1800px")
```

## Photography Credit {.appendix}

<span>Photo by <a href="https://www.tedeytan.com">Ted Eytan</a> on <a href="https://www.flickr.com/photos/taedc/30490299982/in/photolist-NNGFHA-NYZdwa-NwpdCG-NResH2-NYYMEX-NwpnXJ-NYYUYp-NsjKVh-MEQWbW-N29Gmf-ME7Xkd-MEQUEE-MEQSYJ-NbaP55-MEQJaG-MEEvbp-MEQRyE-MEQKJo-NbaMXL-NbaRwj-NbaQ8h-NwoDyA-NRdtkr-NNG3VY-NRdqde-NNFZts-NRenGk-N2a2Zd-NReh84-NVKZxu-N2aGRG-NRe48B-NRejWa-NReiCi-N1SaC2-NNGjL5-N1ScBT-NYZbcF-NRe2Cx-N1Rsdt-N1RgW6-NwoP8A-NRd3fr-N1QYfz-N1Rv9D-NRd8Gi-NYZ3bF">Flickr</a></span>